\tool

### 2018-04-05 paper/paper.tex
Reading group feedback approach, desc, w

\section{Related Work}
%TODO: Use related work from whatever conference committee
Our implementation of \tool~builds on previous research examining recommendation systems in software engineering, techniques for learning new tools and features, approaches for tool recommendations, and existing systems that recommend software engineering tools.

@@

@@

Our approach uses three design pillars to increase awareness of software engineering tools. Our technique \textit{commends} developers for their work, \textit{apprehends} additional opportunities for improvement, and \textit{recommends} useful development tools to improve the code.

@@

\section{Design}

Our three design pillars for \tool~were inspired by previous research in tool recommendations.

Research suggests recommendations between colleagues is the most effective mode of tool discovery. Murphy-Hill and colleagues interviewed software engineers and found that, even though peer interactions occur less frequently in the workplace, developers prefer these user-to-user recommendations over system-to-user interactions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.

To better understand what makes peer interactions an effective mode of tool discovery, Brown and colleagues observed how software users recommend tools to each other while completing tasks to study characteristics of peer interactions. Their results suggest \emph{receptiveness} is a significant factor in determining the outcome of a tool recommendation, while other characteristics such as politeness and persuasiveness are not as important~\cite{vlhcc17}. Fogg argues that a receptive audience is vital for designing persuasive technology, and defines receptiveness as: 1) demonstrating a desire and 2) familiarity with a target behavior~\cite{FoggPersuasive}. Below we explain how our design pillars for \tool~to recommend programming tools to software developers based on their desire and familiarity.

\subsubsection{Demonstrate Desire}

Software developers and users both desire high-quality code without errors. This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging code~\cite{NIST}. Our \textit{commend}

\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

Our goal is for \tool~to increase awareness of software engineering tools. For our initial evaluation in this paper, we target software engineers' desire to produce mistake-free code by automatically recommending \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

\subsubsection{Familiarity}

Choosing an audience familiar with the target behavior is also vital to increasing adoption. To increase use of helpful programming tools, our system focuses on making recommendations to software engineers within the context of the projects they develop. Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}. \tool~uses familiarity with source code to recommend tools to software engineers in code they modify.

To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users. Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.

Don't mention Error Prone or GitHub until here (other than intro).

@@

\subsection{Software Engineering}

\tool~incorporates key software engineering industry concepts to improve tool discovery among software developers.

\subsubsection{Continuous Integration}

Our system utilizes continuous integration to recommend useful tools beforecode changes are integrated into the main repository, or merged. \tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests and commits every 15 minutes. When a new code change is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications. Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds. We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process. \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications implemented (head) to inspect differences. Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work. This also allows our system to easily be integrated into continuous integration builds for software applications to analyze code and recommend development tools to software engineers.

\subsubsection{Debugging}

After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the code modifications. The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if GitHub user code changes fix a reported bug. Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between altered code versions and parse the source code to convert the text into abstract syntax trees.

To determine if an error was fixed, we take several things into consideration: First, our approach ignores errors that are reported as fixed but were not located in files modified by the developer. This ensures that the GitHub user will be familiar with the code change and error fix. Second, we ignore instances where only delete actions were detected between the base and head versions of a file. This avoids making recommendations in situations where bugs are removed but not fixed. For example, a refactoring task such as renaming a class is presented in the GitHub diff as removing code from the original file. This can eliminate bugs reported by Error Prone between code versions, but may also just move the error to another location in the source code. Similarly, we also ignore deprecated classes because the error reported was not fixed. These conditions help us minimize the number of false positives and prevent errant recommendations to developers in our approach.

When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request or commit diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

\subsubsection{Code Review}

Code reviews from co-workers are often standard practice in software development~\cite{CBirdCodeReviewingTrenches}. Pull requests and commits are the primary methods of development contributions and code updates on GitHub~\cite{PullRequestReview}. Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request or commit. \tool~automatically runs software engineering tools and analyzes the code changes, providing feedback to developers based on their changes based on the output from the tool. Github allows users to make comments on specific lines of code changed in pull requests and commits. \tool~leverages this functionality by recommending the tool as a comment at the fix location line from the previous step. Figure 1 presents an example recommendation from our system on a pull request. %TODO: Add screenshot

To increase the likelihood of tool adoption, our system makes recommendations if the tool reports other instances of the fixed error in the latest version of the code. In the comment, \tool~automatically adds direct links to at most two separate locations of the same defect. Our hope is that this encourages developers to use software engineering toolsin their work to fix the similar errors and prevent additional bugs. Additionally, our system uses language similar to a colleage in recommendations. For instance, \tool~uses ``Good job!'' to compliment developers for fixing an error in their work~\cite{?}.

@@

We designed our evaluation to gather quantitative and qualitative data addressing our research questions.

@@

\subsubsection{RQ1}

@@

\subsubsection{RQ2}

@@

\subsection{How often can we expect \tool~to make recommendations?}

@@

\subsection{How useful are recommendations from \tool~to developers?}

>>>>

\section{Related Work}
%TODO: Use related work from whatever conference committee
This work builds on previous research examining recommendation systems in software engineering, techniques for learning new tools, approaches for tool recommendations, and existing automated recommendation systems that recommend software engineering tools.

@@

\section{Motivation}

Our tool recommendation approach is motivated by previous research in tool discovery and peer interactions.

Research suggests recommendations between colleagues is the most effective mode of tool discovery. Murphy-Hill and colleagues interviewed software engineers and found that, even though they appear less frequently in the workplace, developers prefer peer interactions over system-to-user recommendations.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.

To better understand what makes peer interactions effective, Brown and colleagues observed how software users recommend tools to each other while completing tasks. Their results suggest \emph{receptiveness} is a significant factor in determining the outcome of tool recommendations, while other characteristics such as politeness and persuasiveness are not as important~\cite{vlhcc17}. Fogg argues a receptive audience is vital for designing persuasive technology, and describes receptiveness as: 1) demonstrating a desire and 2) familiarity with acquiring a target behavior~\cite{FoggPersuasive}. In this research, our target behavior is the adoption of useful development tools and these two criteria for receptiveness influenced the design principles for our approach for recommending software engineering tools.

@@

Our approach uses three design pillars to increase awareness of software engineering tools: \textit{commend} developers on their work, \textit{apprehend} additional opportunities for improvement, and \textit{recommend} useful development tools to enhance the quality of the code.

Brown and colleages defined demonstrating a desire to adopt a particular behavior as users expressing interest in ``discovering, using, or learning more information'' about a new practice. In software engineering, developers desire to write high-quality programs without errors. This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging programs~\cite{NIST}. Our approach capitalizes on developers' desires to produce mistake-free code by commending developers for their work. Futhermore, psychology research shows that people respond better to praise than blame~\cite{PraiseAndBlame}. To help improve tool adoption among software engineers, our approach analyzes code changes made by developers to determine their intentions, then compliments the developer on their attempt to improve the code quality.

%\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

%Our goal is for \tool~to increase awareness of software engineering tools. For our initial evaluation in this paper, we  recommending \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

Familiarity is also a key part of receptiveness and important in increasing adoption of a target behavior. Fogg suggests users are more likely to adopt a target behavior if they are familiar with it~\cite{FoggPersuasive}. To improve usage of software engineering tools, our approach integrates familiarity. First, we make recommendations based on developers' contributions to recent projects. Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}. Developers should be familiar with the project before making changes to the code base. More specifically, our approach apprehends similar pieces of code the developer may also want to change. After analyzing the code changes and commending the developer on their work, our approach analyzes the entire code base to search for similar opportunities for improvement.

%To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users. Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.

After integrating user receptiveness into our design, the final step is to make a recommendation.

To implement our approach, we developed \tool~to recommend \textsc{Error Prone} to GitHub developers. This section gives an overview describing the general process of how the automated recommendation system works.

@@

@@

This sections provides technical details on the implementation of our approach in \tool. The design of our system is motivated by current practices in the software engineering industry to make \tool~similar to a peer for developers.

\subsection{Continuous Integration}

To analyze developer changes, our system utilizes continuous integration concepts and tools to observe code modifications to GitHub repositories. \tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} We use Jenkins to periodically check for new modifications, commits and pull requests, to GitHub projects every 15 minutes. Our system ignores any commits or pull requests from developers that do not modify a Java file.
When a new code change is found, Jenkins to automatically analyze the patch and run our approach.

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software dependency management tool for Java applications. We automatically inject \textsc{Error Prone} as a Maven plugin to a repository's project object model file (\textit{pom.xml}) and run the build process with the tool. \tool~builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications from the developer (head) to inspect differences. The base and head versions of the source code are tracked using the JGit Java API.\footnote{https://eclipse.org/jgit/}

\subsection{Debugging}

Before commending developers on their work, \tool~must debug to find errors and determine if proposed code changes are a fix. After building the base and head versions with \textsc{Error Prone}, our system parses the output of each build to determine if any faults reported were removed between versions of code. To determine if a change fixes a defect, we developed an algorithm using the code differencing tool GumTree~\cite{GumTree}. GumTree allows us to identify actions (addition, delete, insert, move, and update) performed between the altered versions of the project.

To determine if an error was fixed, we take several things into consideration: First, we ignore errors that are removed but were not located in a file modified by the developer. This ensures that the GitHub user will be familiar with the code changed and potential error fixed. Second, we ignore changes where only delete actions were detected between the base and head versions of a file. This avoids making recommendations in situations where defects were only removed by developers. For example, deleting a class will remove errors reported by \textsc{Error Prone} in the source code, however the intention was not to fix the bugs. Thus, for a change to be considered a fix there must be new code added or existing code modified by the developer. Similarly, we also ignore classes that are deprecated by developers. These conditions were put in place minimize false positives and prevent errant recommendations to software engineers in our approach.

When a fix is identified in the changed version of code, \tool~finds the location of the fix in the head version. To find the modified line of code that fixed a bug, we use GumTree to parse the source code and convert it to abstract syntax trees. We look for the action closest to the offset of the error node determined from the line number reported by \textsc{Error Prone}. If the closest action is not a delete, then our approach uses the location of that action. Otherwise, our algorithm iteratively searches for the closest sibling node or parent nodes that is not a delete action. To apprehend different opportunities for similar changes, we iterate through the list of errors reported by \textsc{Error Prone} in the head version of code and look for instances of the same error that was fixed by the developer.

\subsection{Code Reviews}

Code reviews between developers are a standard procedure of software engineering teams to improve code quality~\cite{CodeReviewingTrenches}. This practice also applies to GitHub projects, with many repositories requiring approval from another developer before changes can be merged into the main code base~\cite{PullRequestReview}. Our approach simulates peer code reviews by making recommendations for static analysis tools as a comment on pull requests and commits. Github allows users to make comments on specific lines of code in situ with the code changes. \tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}.

To increase the likelihood of tool adoption, \tool~implements our approach by commending developers on their changes, apprehending chances for similar modifications, and recommending software engineering tools to find even more related errors. In the comment, \tool~uses language similar to a peer to compliment the author's code contribution. For instance, our system uses ``Good job!'' to commend developers for fixing an error. Additionally, our system presents similar instances of the fixed error found elsewhere in the code.  \tool~automatically adds direct links to at most two different locations of the same defect where a similar fix can be applied. Finally, we recommend \textsc{Error Prone} and provide information about the tool to encourage developers to use software engineering tools in their future work to fix more related errors and more.

@@

To evaluate the effectiveness of our approach, we compared \tool~to different styles and mediums of tool recommendations

@@

\subsubsection{Quantitative}

@@

\subsubsection{Qualitative}

@@

\subsection{Quantitative}

@@

\subsection{Qualitative}
